Combined annotation exploration for SCPCP000006

### 2025-03-17 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
pubs

Here we aim to plot a mean CNV profile across the 35 annotated samples as presented in Figure 1A of [Cresswell et al, bioRxiv (2024)](https://www.biorxiv.org/content/10.1101/2024.09.04.610994v1). 
This represents the mean SNP Array profile of 64 pediatric kidney cancer (including 60 Wilms tumors).

>>>>

Here we aim to plot a mean CNV profile across the 35 annotated samples as presented in Figure 1A of [Cresswell et al. (2024)](https://www.biorxiv.org/content/10.1101/2024.09.04.610994v1). 
This represents the mean SNP Array profile of 64 pediatric kidney cancer (including 60 Wilms tumors).
